Data Exploration: IUCN and AquaMaps

### 2015-09-10 data_explore.Rmd
adding additional chunk for aquamaps only exploration

# Librarires and Paths

@@

lm_eqn <- function(df){
    m <- lm(total_area ~ sm_perc, spp_list);
    eq <- substitute(italic('Total Area') == a + b %.% italic('Percent')*","~~italic(r)^2~"="~r2, 
         list(a = format(coef(m)[1], digits = 2), 
              b = format(coef(m)[2], digits = 2), 
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));                 
}

p1 <- reg + geom_text(x = 50, y = 80000000, label = lm_eqn(spp_list), parse = TRUE)

>>>>

# Libraries and Paths

@@

lm_eqn <- function(df){
    m <- lm(total_area ~ sm_perc, spp_list);
    eq <- substitute(italic('Y') == a + b %.% italic('X')*","~~italic(r)^2~"="~r2, 
         list(a = format(coef(m)[1], digits = 2), 
              b = format(coef(m)[2], digits = 2), 
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));                 
}

p1 <- reg + geom_text(x = 40, y = 300000000, label = lm_eqn(spp_list), parse = TRUE)

print(p1)
```
***

Looking at how many and what type (threat category) of species we are losing by setting a threshold of 0.4 on the aquamaps species.

```{r, warning=F,message=F}

#source mapping aquamaps.R to read in all aquamaps raw data. This takes a while so rendering will take a while. 
source('mapping aquamaps.R')
